Competing Bandits

### 2018-08-15 analysis_code/agents_table.Rmd
add rewrite of paper

dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_full_sim_raw.csv", sep=""))

p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(2000)
priors <- as.list(unique(dat['Prior']))$Prior
warm_starts <-  sort(as.list(unique(dat['Warm.Start']))$Warm.Start, decreasing=FALSE)

>>>>

dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_ht_lhr_3_arms_raw.csv", sep=""))

p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
priors <- as.list(unique(dat['Prior']))$Prior
warm_starts <-  sort(as.list(unique(dat['Warm.Start']))$Warm.Start, decreasing=FALSE)

### 2018-08-15 analysis_code/tournament_table.Rmd
add rewrite of paper

dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_testing_raw.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(1000)
priors <- as.list(unique(dat['Prior']))$Prior

>>>>

dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_ht_lhr_3_arms_raw.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(7000)
priors <- as.list(unique(dat['Prior']))$Prior

### 2018-08-15 paper/competing_bandits.tex
add rewrite of paper

\begin{table}[ht]
\centering
\caption{Reputation Erased Experiment} 
\begin{tabular}{rlll}
  \hline
 & TS & DEG &  DG \\ 
  \hline
TS & \makecell{ \textbf{ 0.18 } $\pm$ 0.042 \\Var:  0.1 \\ ES: 97 \% } & \makecell{ \textbf{ 0.17 } $\pm$ 0.042 \\Var:  0.1 \\ ES: 98 \% } & \makecell{ \textbf{ 0.23 } $\pm$ 0.047 \\Var:  0.2 \\ ES: 98 \% } \\ 
  DEG & \makecell{ \textbf{ 0.23 } $\pm$ 0.045 \\Var:  0.2 \\ ES: 92 \% } & \makecell{ \textbf{ 0.32 } $\pm$ 0.049 \\Var:  0.2 \\ ES: 86 \% } & \makecell{ \textbf{ 0.25 } $\pm$ 0.046 \\Var:  0.2 \\ ES: 90 \% } \\ 
   DG & \makecell{ \textbf{ 0.28 } $\pm$ 0.047 \\Var:  0.2 \\ ES: 87 \% } & \makecell{ \textbf{ 0.33 } $\pm$ 0.051 \\Var:  0.2 \\ ES: 91 \% } & \makecell{ \textbf{ 0.3 } $\pm$ 0.047 \\Var:  0.2 \\ ES: 83 \% } \\ 
   \hline
   \label{rep_erase}
\end{tabular}
\end{table}
% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Sun Jul 22 14:23:06 2018
\begin{table}[ht]
\centering
\caption{Information Erased Experiment} 
\begin{tabular}{rlll}
  \hline
 & TS & DEG &  DG \\ 
  \hline
TS & \makecell{ \textbf{ 0.059 } $\pm$ 0.025 \\Var:  0.05 \\ ES: 97 \% } & \makecell{ \textbf{ 0.11 } $\pm$ 0.033 \\Var:  0.09 \\ ES: 94 \% } & \makecell{ \textbf{ 0.15 } $\pm$ 0.038 \\Var:  0.1 \\ ES: 92 \% } \\ 
  DEG & \makecell{ \textbf{ 0.11 } $\pm$ 0.031 \\Var:  0.08 \\ ES: 89 \% } & \makecell{ \textbf{ 0.19 } $\pm$ 0.038 \\Var:  0.1 \\ ES: 82 \% } & \makecell{ \textbf{ 0.18 } $\pm$ 0.038 \\Var:  0.1 \\ ES: 82 \% } \\ 
   DG & \makecell{ \textbf{ 0.17 } $\pm$ 0.038 \\Var:  0.1 \\ ES: 87 \% } & \makecell{ \textbf{ 0.22 } $\pm$ 0.042 \\Var:  0.1 \\ ES: 82 \% } & \makecell{ \textbf{ 0.26 } $\pm$ 0.043 \\Var:  0.1 \\ ES: 77 \% } \\ 
   \hline
   \label{info_erase}
\end{tabular}
\end{table}

>>>>

\begin{table}[ht]
\centering
\caption{Reputation Erased Experiment} 
\begin{tabular}{rlll}
  \hline
 & TS & DEG &  DG \\ 
  \hline
TS & \makecell{\textbf{ 0.016 } $\pm$ 0.0075 \\Variance: 0.01 \\ ES: 100 \%} & \makecell{\textbf{ 0.13 } $\pm$ 0.02 \\Variance: 0.1 \\ ES: 97 \%} & \makecell{\textbf{ 0.2 } $\pm$ 0.024 \\Variance: 0.1 \\ ES: 96 \%} \\ 
  DEG & \makecell{\textbf{ 0.068 } $\pm$ 0.013 \\Variance: 0.05 \\ ES: 93 \%} & \makecell{\textbf{ 0.29 } $\pm$ 0.024 \\Variance: 0.2 \\ ES: 75 \%} & \makecell{\textbf{ 0.26 } $\pm$ 0.024 \\Variance: 0.2 \\ ES: 80 \%} \\ 
   DG & \makecell{\textbf{ 0.15 } $\pm$ 0.019 \\Variance: 0.1 \\ ES: 87 \%} & \makecell{\textbf{ 0.38 } $\pm$ 0.028 \\Variance: 0.2 \\ ES: 80 \%} & \makecell{\textbf{ 0.33 } $\pm$ 0.024 \\Variance: 0.2 \\ ES: 67 \%} \\ 
   \hline
   \label{rep_erase}
\end{tabular}
\end{table}
% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Sun Jul 22 14:23:06 2018
\begin{table}[ht]
\centering
\caption{Information Erased Experiment Heavy Tail X=200} 
\begin{tabular}{rlll}
  \hline
 & TS & DEG &  DG \\ 
  \hline
TS & \makecell{\textbf{ 0.024 } $\pm$ 0.0094 \\Variance: 0.02 \\ ES: 100 \%} & \makecell{\textbf{ 0.16 } $\pm$ 0.022 \\Variance: 0.1 \\ ES: 97 \%} & \makecell{\textbf{ 0.22 } $\pm$ 0.025 \\Variance: 0.2 \\ ES: 95 \%} \\ 
  DEG & \makecell{\textbf{ 0.24 } $\pm$ 0.025 \\Variance: 0.2 \\ ES: 94 \%} & \makecell{\textbf{ 0.29 } $\pm$ 0.024 \\Variance: 0.1 \\ ES: 72 \%} & \makecell{\textbf{ 0.27 } $\pm$ 0.024 \\Variance: 0.1 \\ ES: 76 \%} \\ 
   DG & \makecell{\textbf{ 0.33 } $\pm$ 0.028 \\Variance: 0.2 \\ ES: 94 \%} & \makecell{\textbf{ 0.38 } $\pm$ 0.026 \\Variance: 0.2 \\ ES: 74 \%} & \makecell{\textbf{ 0.33 } $\pm$ 0.023 \\Variance: 0.1 \\ ES: 58 \%} \\ 
   \hline
   \label{info_erase}
\end{tabular}
\end{table}
